---
title: "Chapter 2 Thoughts and Solutions"
author: "Rigel"
date: "October 10, 2017"
output: 
  html_document: 
    keep_md: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction to Statistical Learning Chapter 2 - Thoughts and Solutions
#Questions 1
 
I think the word "generally"" is quite important here.

a) Large n and small p, we would expect a more flexible method to provide a better fit because it is fitting the data more closely without having the effect of overfitting increasing the error as much. 


b) Large p and small n, we would expect a LESS flexible method to provide a better fit because it is more robust and therefore less likely to overfit. 

- In other words, the decrease in bias would be bigger than the increase in variance when n is huge and p is small. THis relationship is reversed if the condition is reversed. 

Note: IF p>n there won't be a unique solution for least square so it wouldn't even work. 

THink of solving x+y+z = 10 and 2x+3y+4z = 25

c) if the true underlyinig relationship is non - linear, this would mean we expect a linear method to perform badly at the predicting. 

d) The variance of the error is high which suggest there is a lot of noise, a more flexible method will tend to overadjust to these noises and thus provide a model that would overfit the data. A less flexible will be more robust to overfitting and thus perform better in this instance. (SEE Experiment folder)



```{r cars}


```

## Question 2

####Note: We tend to refer to problems with a quantitative response as regression problems, while those involving a qualitative response are often referred to as classi???cation problems

a) CEO's salary is quantitative and thus this is a regression problem. Since we are interested in the relationship between n and p, this can be treated as an inference problem. n = 500, p = profit, number of employees, industry (3)

b) The response, success and failure is a qualitative and thus it is a classification problem, we are interested in the outcome and thus this can be treated as a prediction problem as well. n = 20, p = priced charged, marketing budget, competition price, and ten other variables ~ p = 13.

c) the response is quantitative so this is a regression problem. THis is also a prediction problem as we try to predict the future market rates.  n = 52 , p = % change in dollar, % change in us market,% change in british market, % change in german market. p = 4

## Question 3



## Question 4

###Classification

Note:: Classification problems is when the response is qualitative other than quantitative - Prediction is when we create f(x) and uses it onto new data points. Inference is when we try to understand f(x)

4.1.1) Classifying what type of cancer a patient have given their genes data. This is a prediction problem, genes data is the features and the response is types of cancer. 

4.1.2)We can transform this into a inference problem if we try to understand which genes mutation causes which type of cancer



4.2.1) Classifying Email spam base on words in the email, the features are the words, and reponse is Yes/No on the spam. ()

4.2.2)We can transform this into an inference problem if we try to understand which words causes an email to be classified as spam.

4.3.1) Classifying different words from amplitude recorded from a device. (Speech Recognition) The response is different words and the feature is the amplitude recorded

4.3.2) We can transform this into an inference problem if we try to understand how different movement in the amplitude turns into different words.

###Regression

4.4.1)  Trying to predict weight using height - 

4.4.2) If we are trying to understand how height affects weight this is an inference problem

4.5.1) Trying to predict supermarket sales using the number of cars in the car park.

4.5.1) If we are trying to understand how number of cars in the car park affect sales this is an inference problem

4.6.1) Trying to predict a house's price base on its size. 

4.6.2) If we are trying to understand how a house's size affect its price then this is an inference problem. 




###Clustering


http://home.deib.polimi.it/matteucc/Clustering/tutorial_html/
Possible Applications
Clustering algorithms can be applied in many fields, for instance:

Marketing: finding groups of customers with similar behavior given a large database of customer data containing their properties and past buying records;
Biology: classification of plants and animals given their features;
Libraries: book ordering;
Insurance: identifying groups of motor insurance policy holders with a high average claim cost; identifying frauds;
City-planning: identifying groups of houses according to their house type, value and geographical location;
Earthquake studies: clustering observed earthquake epicenters to identify dangerous zones;
WWW: document classification; clustering weblog data to discover groups of similar access patterns.
 
## Question 5

A very flexible model will provide a better fit if the underlying relationship is rather complicated and can not be explained well by a simpler model. <<< In this case the decrease in bias as the model gets more flexible is greater than the increase in variance.

However, a less flexible method might be better if the underlying relationship is less complicated, it is much more robust and less likely to overfit the data. 

Generally speaking, a less flexible method might be preferred if we dealing with an inference problem, however, a more flexible model is usually better at predictting. 

##Question 6

##Question 7


```{r}

```





