---
title: "Chapter 2 Thoughts and Solutions"
author: "Rigel"
date: "October 10, 2017"
output: 
  html_document: 
    keep_md: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction to Statistical Learning Chapter 2 - Thoughts and Solutions
#Questions 1
 
I think the word "generally"" is quite important here.

a) Large n and small p, we would expect a more flexible method to provide a better fit because it is fitting the data more closely without having the effect of overfitting increasing the error as much. 


b) Large p and small n, we would expect a LESS flexible method to provide a better fit because it is more robust and therefore less likely to overfit. 

- In other words, the decrease in bias would be bigger than the increase in variance when n is huge and p is small. THis relationship is reversed if the condition is reversed. 

Note: IF p>n there won't be a unique solution for least square so it wouldn't even work. 

THink of solving x+y+z = 10 and 2x+3y+4z = 25

c) if the true underlyinig relationship is non - linear, this would mean we expect a linear method to perform badly at the predicting. 

d) The variance of the error is high which suggest there is a lot of noise, a more flexible method will tend to overadjust to these noises and thus provide a model that would overfit the data. A less flexible will be more robust to overfitting and thus perform better in this instance. (SEE Experiment folder)



```{r cars}


```

## Question 2

####Note: We tend to refer to problems with a quantitative response as regression problems, while those involving a qualitative response are often referred to as classi???cation problems

a) CEO's salary is quantitative and thus this is a regression problem. Since we are interested in the relationship between n and p, this can be treated as an inference problem. n = 500, p = profit, number of employees, industry (3)

b) The response, success and failure is a qualitative and thus it is a classification problem, we are interested in the outcome and thus this can be treated as a prediction problem as well. n = 20, p = priced charged, marketing budget, competition price, and ten other variables ~ p = 13.

c) the response is quantitative so this is a regression problem. n = 52 , p = % change in dollar, % change in us market,% change in british market, % change in german market. p = 4

## Question 3

## Question 4
 






```{r}

```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.



